Of judges, aliens and total preorders

### 2021-02-08 paper/1901_3230880_philip_heltweg.tex
feat: rewritten discussion example

Darwiche and Pearl show that their version of belief revision on epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$. The mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment. As Booth and Meyer describe an additional structure, from which a tpo $\leq_{\mathbb{E}}$ can be determined, faithful assignment is mentioned here only for completeness. For more information refer to Katsuno and Mendelzon \cite{Katsuno1991}.

@@

    % TODO tpo alpha ast beta is unlucky because ast has a different meaning already, also change in figure 8 caption
    Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed. After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in Figure \ref{fig:example-preceq-revised-alien2}.

@@

% TODO: this critique example seems very weak
Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened. Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not. Consider the following situation in our courtroom Example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder. $\alpha$  makes a world $x$, with $p$ being true, more likely. But, because of a large body of evidence, the judge still considers a world $y$, where Mary is the murderer, to be more plausible. This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:

@@

But what if evidence is submitted that, if Mary is the murderer, the victim must be an alien $\gamma = q \implies r$? Semantically a human agent would assume all worlds in which Mary is the murderer to be highly unlikely due to how far fetched the acceptance of the victim being an alien is. Further research is required to solve this apparent contradiction by modelling different types and strengths of evidence.

>>>>

Darwiche and Pearl show that their version of belief revision on epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$. A mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment. As Booth and Meyer describe an additional structure, from which a tpo $\leq_{\mathbb{E}}$ can be determined, faithful assignment is mentioned here only for completeness. For more information refer to Katsuno and Mendelzon \cite{Katsuno1991}.

@@

    Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed. After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in Figure \ref{fig:example-preceq-revised-alien2}.

@@

% TODO: this critique example seems very weak
Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened. Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
Consider the following situation in a world described by the set of propositional variables $\{x_1, x_2, x_3, y\}$: New evidence $\alpha = x_1$ arrives that  makes a world $x$, with $x_1$ being true, more likely. But, because $\alpha$ is just one piece of fairly unspecific evidence among many, the agent still considers a world $y$ to be more plausible. This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:

@@

But what if evidence is submitted, for example $\gamma = x_1 \wedge x_2 \wedge x_3$? Because $\gamma$ is more specific ($|\modelsOf{\gamma}| <  |\modelsOf{\alpha}|$) a human might consider it semantically stronger in favour of the worlds in $\modelsOf{\gamma}$. Because all worlds in $\modelsOf{\gamma}$ are also in $\modelsOf{\alpha}$, and the agent has already established no evidence can change their mind due to \ref{AST7}, even this very specific evidence can not change the relative ordering of worlds. Different operators might weaken \ref{AST6} and \ref{AST7} to solve this apparent contradiction by modelling different strengths of evidence.
